Demanding resources: Converging characteristics of challenge and resource

### 2022-10-14 copy of SIOP2023convergence.Rmd
job cat graphs although looks like pulled from wrong object

```{r workcat}
## Job classifications

ggplot(workers, aes(O.Net.Job.Family.Categories))+
  geom_histogram(stat="count") + coord_flip()

ggplot(workers, aes(O.Net.Job.Family.Categories)) +
  geom_histogram(stat="count") + coord_flip()

dataworker <- cbind(data,workers)    ## to repeat O*Net analyses
                                     ## This gets worker info into convergence file

@@

>>>>

@@

```{r workcat, fig.cap="Percent agreement (resource and challenge) across O*Net occupational categories (probably need to revisit original coding).", fig.height=10}

## Job classifications

# ggplot(workers, aes(O.Net.Job.Family.Categories))+
#   geom_histogram(stat="count") + coord_flip()

#ggplot(workers, aes(O.Net.Job.Family.Categories)) +
#  geom_histogram(stat="count") + coord_flip()

dataworker <- cbind(anova,workers)    ## to repeat O*Net analyses
                                     ## This gets worker info into convergence file

dataworker$overall <- rowMeans(dataworker[1:84], na.rm=TRUE)

ggplot(dataworker, aes(x=overall)) + geom_histogram() + facet_wrap(~O.Net.Job.Family.Categories, nrow=8)

### 2022-10-14 copy-of-SIOP2023convergence.tex
job cat graphs although looks like pulled from wrong object

\includegraphics{copy-of-SIOP2023convergence_files/figure-latex/workcat-1.pdf} \includegraphics{copy-of-SIOP2023convergence_files/figure-latex/workcat-2.pdf}

@@

>>>>

@@

\begin{figure}
\centering
\includegraphics{copy-of-SIOP2023convergence_files/figure-latex/workcat-1.pdf}
\caption{\label{fig:workcat}Percent agreement (resource and challenge) across O*Net occupational categories (probably need to revisit original coding).}
\end{figure}
